---
title: "Doing Reproducible Research with R"
author: "Joonion Bae"
date: '2022-05-23'
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Writing with Markdown

Publish or perish! \
\
This is an **important** note to a *researcher*. \

### Publish or perish!  

#### Publish or perish!  

##### Publish or perish!  

How to publish not to be perished?

1. Do your research.
2. Write your paper.
3. Submit to a journal
    - If accepted, goto 1.
    - If not accpted, goto 1.

R 마크다운 문서는 마크다운 문법을 사용합니다. 마크다운은 아주 간단한 문법으로 문서의 형식을 지정할 수 있으며, HTML, PDF, Word 문서로의 변환도 간단합니다. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

RStudio의 상단에 있는 **Knit** 버튼을 누르면 HTML, PDF, Word 문서를 생성할 수 있습니다. 

### 분석결과 포함하기

```{r summary}
library(palmerpenguins)
library(tidyverse)
penguins %>%
    group_by(species) %>%
    summarise(across(where(is.numeric), mean, na.rm = T))
```

### 표와 그림 포함하기

마크다운 문서 안에 **표**도 포함할 수 있습니다.

```{r tables}
library(stargazer)
stargazer(data.frame(penguins), type="text")
```

마크다운 문서 안에 **그림**도 포함할 수 있습니다.

```{r figures, echo=FALSE}
ggplot(data = penguins, 
       mapping = aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(aes(color = species, shape = species), size = 3, alpha = 0.8) +
  scale_color_manual(values = c("darkorange","purple","cyan4")) +
  labs(title = "Penguin size, Palmer Station LTER",
       subtitle = "Flipper length and body mass for Adelie, Chinstrap and Gentoo Penguins",
       x = "Flipper length (mm)",
       y = "Body mass (g)",
       color = "Penguin species",
       shape = "Penguin species") +
  theme_minimal()
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
